NumPy---Array Programming in Python

### 2020-01-31 body.tex
Trivial edits to interop

NumPy provides in-memory, multidimensional, homogeneously typed
(i.e., single pointer and strided) arrays on CPUs.
It runs on machines ranging from embedded devices to the world's
largest supercomputers and yields performance
approaching that of compiled languages.
For algorithms that do not fit the array programming approach,
or require even faster implementations, a variety of tools exist (e.g., Cython, Numba, Pythran)
that transparently accelerate bottlenecks.
These tools allow programmers to express concepts using high level array programming without sacrificing efficiency.
In many cases, fast algorithms already are implemented by libraries in the scientific Python ecosystem; using these primitives, efficient codes can be written in pure Python.
% smooth experience/intengration from high level <-> low level?

@@

Importantly, some projects chose to follow the NumPy API exactly---with Dask,
CuPy, Sparse and JAX the most prominent examples---while others have
NumPy-inspired semantics but chose to deviate in places.
% when they deviate, they sometimes fix it, e.g.,
% https://github.com/pytorch/pytorch/pull/1983
% https://github.com/pytorch/pytorch/issues/2228
% many have for numpy users
% https://github.com/torch/torch7/wiki/Torch-for-Numpy-users

>>>>

NumPy provides in-memory, multidimensional, homogeneously typed
(i.e., single pointer and strided) arrays on CPUs.
It runs on machines ranging from embedded devices to the world's
largest supercomputers, with performance
approaching that of compiled languages.
For algorithms that do not fit the array programming approach,
or require even faster implementations, a variety of tools exist (e.g., Cython, Numba, Pythran)
that transparently accelerate bottlenecks.
These tools allow programmers to express concepts using high level array programming without sacrificing efficiency.
In many cases, fast algorithms already are implemented by libraries in the scientific Python ecosystem; using these primitives, efficient codes can be written in pure Python.
% smooth experience/intengration from high level <-> low level?

@@

Importantly, some projects follow the NumPy API exactly---with Dask,
CuPy, Sparse and JAX the most prominent examples---while others have
NumPy-inspired semantics but, often due to their development history, deviate in places.
% when they deviate, they sometimes fix it, e.g.,
% https://github.com/pytorch/pytorch/pull/1983
% https://github.com/pytorch/pytorch/issues/2228
% many have for numpy users
% https://github.com/torch/torch7/wiki/Torch-for-Numpy-users
